---
title: "Between and Within-level Variations in Delta-Beta Synchrony"
author: "Berenice Anaya"
date: "8/21/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

List of necessary packages
```{r}
list.of.packages <- c("tidyverse", "psych", "ggplot2","RColorBrewer","gcookbook", "lme4","nlme",
                      "effects", "backports", "interactions", "corrplot", "lmerTest")
```

```{r, include=FALSE}
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
# Loading packages
lapply(list.of.packages, require, character.only = TRUE)
```


# Data Preparation

Reading the Person-level data
```{r}
path="C:/Users/bua25/Documents/BRAIN project/SecondbySecond/"
setwd(path)

#questionnaires
QST<-read.csv("BRAINquestionnaires.csv", header = T)
QST<-QST[, c(1,32:34,36,38,40,43,154,208)]
colnames(QST)[1]<-"id"

#Demographics
Demo<-read.csv("BRAINS_Demographics.csv", header = T)
Demo<-Demo[, c(1,4,5,25)]
colnames(Demo)[1]<-"id"

#Social Reticence and Dyad ids
dyad<- read.csv("BehComp.csv", header = T)
dID<-read.csv("BLNdyadIds.csv", header =T)

#Mergin person-level variables
Pdata<-merge(Demo, QST, by="id")
```



The person level data include a larger number of participants, who provided BIQ data but were either not enrolled in the study, or were not part of the Baseline wave.
Next we narrow the Person level data to the number of participants who actually have repeated measures of EEG

Second-by-second level data (T= 1-284)
```{r}
#reading repeated EEG power data
DBs<-read.csv("DBsecbysec.csv", header = T)

#adding variable for number of segments
DBs<- DBs%>%
 dplyr::group_by(id)%>%
  dplyr::add_tally()

#subseting the segment variable as unique to each participant
EEGseg<- DBs%>%
  dplyr::select(id, n) %>% unique()
#merging this subset into the Pdata to reduce to the number of actual participants with EEG data
Pdata<-merge(Pdata, EEGseg, by="id")
Pdata<-Pdata[, c(1,5:14)]
#Pdata<-Pdata[-51,]

enrolled<-read.csv("BRAINSenrolledCorrectNumbers.csv")
Pdata<-merge(enrolled, Pdata, by="id")
Pdata<-Pdata[-89,]
```



Person level data now contains all the participants who also have data for the EEG data
```{r}
Pdata$ScaredSoc.c <- scale(Pdata$SCARED_P_psocphf_P_BLN, center=TRUE, scale=FALSE)
Pdata$ScaredSep.c <- scale(Pdata$SCARED_P_psepax_P_BLN, center=TRUE,scale=FALSE)
Pdata$ScaredGen.c <- scale(Pdata$SCARED_P_pgenax_P_BLN, center=TRUE,scale=FALSE)
Pdata$ScaredTot.c <- scale(Pdata$SCARED_P_psctotal_P_BLN, center=TRUE,scale=FALSE)
Pdata$BIQ.c <- scale(Pdata$Total_BIQ, center = TRUE, scale = FALSE)


describe(Pdata)
```


Between- and within- components

We now split the time-varying predictor into “trait” (between-person differences) and “state” (within-person deviations) components. Specifically, the reapeated variables of Delta and Beta power are split into two varaibles: Delta_trait is the sample-mean centered between-person component, and Delta_state is the person-centered within-person component.
```{r}
#Person-level Delta
FDelta_imeans <- DBs %>% 
                  group_by(id) %>%
  dplyr::summarise(FDelta_trait=mean(FrontalDelta, na.rm=TRUE))
                  

CDelta_imeans <- DBs %>% 
                  group_by(id) %>% 
                  dplyr::summarize(CDelta_trait=mean(CentralDelta, na.rm=TRUE))

PDelta_imeans <- DBs %>% 
                  group_by(id) %>% 
                  dplyr::summarize(PDelta_trait=mean(ParietalDelta, na.rm=TRUE))


#merging into person-level file
Pdata <- merge(Pdata, FDelta_imeans, by="id")  
Pdata <- merge(Pdata, CDelta_imeans, by="id") 
Pdata <- merge(Pdata, PDelta_imeans, by="id") 

#getting rid of duplicate case
Pdata<-Pdata[-51,]

#make centered versions of the person-level scores
Pdata$FDelta_trait_c <- scale(Pdata$FDelta_trait,center=TRUE,scale=FALSE)
Pdata$CDelta_trait_c <- scale(Pdata$CDelta_trait,center=TRUE,scale=FALSE)
Pdata$PDelta_trait_c <- scale(Pdata$PDelta_trait,center=TRUE,scale=FALSE)

#describe person-level data
describe(Pdata)



#Repeating the same for Beta power
#Person-level Delta
FBeta_imeans <- DBs %>% 
                  group_by(id) %>% 
                  dplyr::summarize(FBeta_trait=mean(FrontalBeta, na.rm=TRUE))

CBeta_imeans <- DBs %>% 
                  group_by(id) %>% 
                  dplyr::summarize(CBeta_trait=mean(CentralBeta, na.rm=TRUE))

PBeta_imeans <- DBs %>% 
                  group_by(id) %>% 
                  dplyr::summarize(PBeta_trait=mean(ParietalBeta, na.rm=TRUE))


#merging into person-level file
Pdata <- merge(Pdata, FBeta_imeans, by="id")  
Pdata <- merge(Pdata, CBeta_imeans, by="id") 
Pdata <- merge(Pdata, PBeta_imeans, by="id") 

#make centered versions of the person-level scores
Pdata$FBeta_trait_c <- scale(Pdata$FBeta_trait,center=TRUE,scale=FALSE)
Pdata$CBeta_trait_c <- scale(Pdata$CBeta_trait,center=TRUE,scale=FALSE)
Pdata$PBeta_trait_c <- scale(Pdata$PBeta_trait,center=TRUE,scale=FALSE)

#describe person-level data
describe(Pdata)

```


Making state variables in long data (as deviations from uncentered trait variable)
```{r}
#merging person-level data into daily data
DBlong <- merge(DBs,Pdata,by="id")

#calculating state variables for Delta
DBlong$FDelta_state <- DBlong$FrontalDelta - DBlong$FDelta_trait
DBlong$CDelta_state <- DBlong$CentralDelta - DBlong$CDelta_trait
DBlong$PDelta_state <- DBlong$ParietalDelta - DBlong$PDelta_trait

#calculating state variables for Beta
DBlong$FBeta_state <- DBlong$FrontalBeta - DBlong$FBeta_trait
DBlong$CBeta_state <-  DBlong$CentralBeta - DBlong$CBeta_trait
DBlong$PBeta_state <-  DBlong$ParietalBeta - DBlong$PBeta_trait

#describing data
describe(DBlong)
```

# Descriptive analyses of Delta and Beta power

We now computing power means in a wide dataset, to assess mean differences in EEG power across regions, demographic variables, and task condition
```{r}

func <- function(DBlong)
{
  return(data.frame(FD = mean(DBlong$FrontalDelta),
                    CD = mean(DBlong$CentralDelta),
                    PD = mean(DBlong$ParietalDelta),
                    FB = mean(DBlong$FrontalBeta),
                    CB = mean(DBlong$CentralBeta),
                    PB = mean(DBlong$ParietalBeta)))
}
library(plyr)
Power<-ddply(DBlong, .(id, condition), func)

#checking the condition variable
table(Power$condition)
#recoding the wrong labels
Power$condition[Power$condition=="L_"] <- "CL"
Power$condition[Power$condition=="P_"] <- "OP"
```

Analyses of Variance (ANOVAs) testing EEG power differences across eyes-open/ eyes-closed conditions
```{r}
#Delta across regions
summary(aov(FD ~ condition + 
              Error(id/condition), data=Power))

summary(aov(CD ~ condition + 
              Error(id/condition), data=Power))
summary(aov(PD ~ condition + 
              Error(id/condition), data=Power))
#Beta across regions
summary(aov(FB ~ condition + 
              Error(id/condition), data=Power))

summary(aov(CB ~ condition + 
              Error(id/condition), data=Power))
summary(aov(PB ~ condition + 
              Error(id/condition), data=Power))
```



We now melt or shape this data set by region, in order to test power differences across regions with a repeated mmeasures ANOVA
```{r}
#melting by region
Power<- Power %>%
  group_by(id)%>%
  dplyr::summarise(mean(FD),
                   mean(CD),
                   mean(PD),
                   mean(FB),
                   mean(CB),
                   mean(PB))

demovars<- Pdata[, c("id","Gender","Ethnicity","age.BLNinyears","BI","Total_BIQ")]
Power<-merge(Power,demovars, by="id")

colnames(Power)<-c("id","Delta_F","Delta_C", "Delta_P","Beta_F","Beta_C", "Beta_P","Gender",
                   "Eth","Age","BI","TotalBIQ")

#removing extra row that participant 3165 creates
Power<-Power[-48,]
  
powerLong<- reshape(Power,
                    timevar = "BrainRegion",
                    varying = c("Delta_F","Delta_C", "Delta_P","Beta_F","Beta_C", "Beta_P"),
                    idvar = "id",
                    sep = "_",
                    direction = "long")
```


Testing BI, gender, and ethnicity differences
```{r}
#Differences in Delta power
summary(aov(Delta ~ BrainRegion*Gender + BrainRegion*TotalBIQ, data=powerLong)) #sig between BI, higher for BI and higher for Boys
#means
describeBy(powerLong$Delta, group = powerLong$Gender)
describeBy(powerLong$Delta, group = powerLong$BI)
describeBy(powerLong$Delta, group = powerLong$BrainRegion)
#ethnicity
summary(lm(Delta ~ BrainRegion*Eth, data=powerLong, na.action = na.exclude)) #not sig between ethnic groups

#Differences in Beta power
summary(aov(Beta ~ BrainRegion*Gender + BrainRegion*TotalBIQ, data=powerLong)) #sig between BI, higher for BI and for boys
#means
describeBy(powerLong$Beta, group = powerLong$Gender)
describeBy(powerLong$Beta, group = powerLong$BI)
describeBy(powerLong$Beta, group=powerLong$BrainRegion)
#ethnicity
summary(lm(Beta ~ BrainRegion*Eth, data=powerLong, na.action = na.exclude)) #not sig between ethnic groups
```

We now compute mean level stability of Delta and Beta power across regions
```{r}
#Delta
print(corr.test(Power[,c(2:4)], 
                use = "pairwise",method="pearson",adjust="holm", alpha=.05,ci=TRUE), 
      short=FALSE)
cor.test(Power$Delta_F, Power$Delta_C, method = "pearson")
#visual
pairs.panels(Power[,c(2:4)])

#Beta
print(corr.test(Power[,c(5:7)], 
                        use = "pairwise",method="pearson",adjust="holm", alpha=.05,ci=TRUE), 
              short=FALSE)
pairs.panels(Power[,c(5:7)])
```


# Delta-Beta synchrony overtime
Before examining inter and intraindividual variability, we examine the effect of time (in seconds) spent in the resting state task on delta-beta synchrony.
```{r}

Bc<-lmeControl(maxIter = 100, msMaxIter = 100, tolerance = 1e-6, niterEM = 50,
              msMaxEval = 400,
              msTol = 1e-7, msVerbose = FALSE,
              returnObject = FALSE, gradHess = TRUE, apVar = TRUE,
              .relStep = .Machine$double.eps^(1/3), minAbsParApVar = 0.05,
              opt = "optim")

#frontal
model_time.f <- lme(FDelta_state ~ 1 + FBeta_state + seconds +
                      FBeta_state:seconds,
                    random = ~ 1 + FBeta_state + seconds |id,
                    data = DBlong, 
                    control = Bc,
                    na.action = na.exclude)
summary(model_time.f)

#central
model_time.c <- lme(CDelta_state ~ 1 + CBeta_state + seconds +
                      CBeta_state:seconds,
                    random = ~ 1 + CBeta_state + seconds |id,
                    data = DBlong, 
                    control = Bc,
                    na.action = na.exclude)
summary(model_time.c)


#parietal
model_time.p <- lme(PDelta_state ~ 1 + PBeta_state + seconds +
                      PBeta_state:seconds,
                    random = ~ 1 + PBeta_state + seconds |id,
                    data = DBlong, 
                    control = Bc,
                    na.action = na.exclude)
summary(model_time.p)
```


# Variability in Delta power

Unconditional means models reveal how much individual variation is the outcome measures, as estimated by the ICC. We ran these models on Delta power, which was the variable placed on the outcome side of the equation. This choice was arbitrary, as we are interested in the synchrony of delta and beta power, so either Delta or Beta could have been placed on the outcome. 
```{r}
#Frontal
model0_fit <- lmer(formula = FrontalDelta ~ 1 + (1|id), 
              data=DBlong,
              na.action=na.exclude)
summary(model0_fit)
VarCorr(model0_fit)
RandomEffects <- as.data.frame(VarCorr(model0_fit))
RandomEffects
ICC_between <- RandomEffects[1,4]/(RandomEffects[1,4]+RandomEffects[2,4]) 
ICC_between
```
From the unconditional means model, the ICC was calculated, which indicated that of the total variance in Frontal Delta power, 21.79% is attributable to between-person variation whereas 78.21% is attributatable to within-person variation.

```{r}
#Central
model0_fit <- lmer(formula = CentralDelta ~ 1 + (1|id), 
              data=DBlong,
              na.action=na.exclude)
summary(model0_fit)
VarCorr(model0_fit)
RandomEffects <- as.data.frame(VarCorr(model0_fit))
RandomEffects
ICC_between <- RandomEffects[1,4]/(RandomEffects[1,4]+RandomEffects[2,4]) 
ICC_between
```
For Central Delta power 41.73% is attributable to between-person variation and only 58.27% attributable to within person variation

```{r}
#Parietal Delta
model0_fit <- lmer(formula = ParietalDelta ~ 1 + (1|id), 
              data=DBlong,
              na.action=na.exclude)
summary(model0_fit)
VarCorr(model0_fit)
RandomEffects <- as.data.frame(VarCorr(model0_fit))
RandomEffects
ICC_between <- RandomEffects[1,4]/(RandomEffects[1,4]+RandomEffects[2,4]) 
ICC_between
```

For Parietal Delta power 45.86% is attributable to between-person variation and only 54.14% attributable to within person variation



# Between and within-person differences

Multilevel models examining Between and within-person differences in Delta~Beta synchrony
Model for Frontal region
```{r}
model1_fit <- lmer(formula = FrontalDelta ~ 1 + seconds + FBeta_trait_c + 
                      FBeta_state + FBeta_state:FBeta_trait_c +
                      (1 + FBeta_state|id), 
                    data=DBlong,
                    na.action=na.exclude)
summary(model1_fit)


#Visual
ggplot(data=DBlong, aes(x=FBeta_state, y=FDelta_state, group=factor(id), color=FBeta_trait_c), legend=FALSE) +
  geom_smooth(method=lm, se=FALSE, fullrange=FALSE, lty=1, size=.7) +
  scale_color_viridis_c("Trait Beta Power")+
  geom_smooth(aes(group=1), method=lm, se=FALSE, fullrange=FALSE, lty=1, size=1.5, color="black") +
  xlab("Beta Power State") + ylab("Predicted State Delta Power") +
  theme_classic() +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Within-Person Delta-Beta Synchrony")

```

Central synchrony model
```{r}
model1_fit <- lmer(formula = CentralDelta ~ 1 + seconds + CBeta_trait_c + 
                      CBeta_state + CBeta_trait_c:CBeta_state +
                      (1 + CBeta_state|id), 
                    data=DBlong,
                    na.action=na.exclude)
summary(model1_fit)
```

Parietal synchrony 
```{r}
model1_fit <- lmer(formula = ParietalDelta ~ 1 + seconds + PBeta_trait_c + 
                      PBeta_state + PBeta_trait_c:PBeta_state +
                      (1 + PBeta_state|id), 
                    data=DBlong,
                    na.action=na.exclude)
summary(model1_fit)
```


# Delta-Beta Synchrony and Behavioral Inhibition
Multilevel models examining if and how between person differences in BI are related to trait and state-level synchrony


Frontal synchrony and Continuous BI
```{r}
model1_fit <- lmer(formula = FrontalDelta ~ 1 + FBeta_trait_c + FBeta_state + BIQ.c +
                     FBeta_trait_c:BIQ.c + FBeta_state:BIQ.c + FBeta_trait_c:FBeta_state +
                     FBeta_trait_c:FBeta_state:BIQ.c +
                      (1 + FBeta_state|id), 
                    data=DBlong,
                    na.action=na.exclude)
summary(model1_fit)
```

Central synchrony and BIQ
```{r}
model1_fit <- lmer(formula = CentralDelta ~ 1 + CBeta_trait_c + CBeta_state + BIQ.c +
                     CBeta_trait_c:BIQ.c + CBeta_state:BIQ.c + CBeta_trait_c:CBeta_state + 
                     CBeta_trait_c:CBeta_state:BIQ.c+
                      (1 + CBeta_state|id), 
                    data=DBlong,
                    na.action=na.exclude)
summary(model1_fit)
```


Parietal synchrony and BIQ
```{r}
model1_fit <- lmer(formula = ParietalDelta ~ 1 + PBeta_trait_c + PBeta_state + BIQ.c +
                     PBeta_trait_c:BIQ.c + PBeta_state:BIQ.c + PBeta_trait_c:PBeta_state + 
                     PBeta_trait_c:PBeta_state:BIQ.c+
                      (1 + PBeta_state|id), 
                    data=DBlong,
                    na.action=na.exclude)
summary(model1_fit)
```



# Delta-Beta synchrony and BI temperament profiles
Frontal synchrony and BI
```{r}
DBlong$BI<-as.factor(DBlong$BI)
model1_fit <- lmer(formula = FrontalDelta ~ 1 + FBeta_trait_c + FBeta_state + BI +
                     FBeta_trait_c:BI + FBeta_state:BI + FBeta_trait_c:FBeta_state +
                     FBeta_trait_c:FBeta_state:BI +
                      (1 + FBeta_state|id), 
                    data=DBlong,
                    na.action=na.exclude)
summary(model1_fit)
```

Central synchrony and BI
```{r}
model1_fit <- lmer(formula = CentralDelta ~ 1 + CBeta_trait_c + CBeta_state + BI +
                     CBeta_trait_c:BI + CBeta_state:BI + CBeta_trait_c:CBeta_state + 
                     CBeta_trait_c:CBeta_state:BI+
                      (1 + CBeta_state|id), 
                    data=DBlong,
                    na.action=na.exclude)
summary(model1_fit)
```

# Visualization of state-level synchrony and BI at central region
Here we show a synchrony pattern for a BI child vs. a BN child along with a simple slopes graph of the interaction
```{r}
model3a_fit <- lme4::lmer(formula = CentralDelta ~ 1 + CBeta_trait_c + CBeta_state + BI +
                     CBeta_trait_c:BI + CBeta_state:BI + CBeta_trait_c:CBeta_state + 
                     CBeta_trait_c:CBeta_state:BI+
                      (1 + CBeta_state|id), 
                    data=DBlong,
                    na.action=na.exclude)
summary(model3a_fit)

ggplot(data = DBlong, aes(x=CBeta_state, y=CentralDelta, color=BI))+
  geom_smooth(method="lm", fullrange=TRUE, na.rm = T, se=F)+
  scale_color_viridis_d("BI",end = .9)+
  xlab("State-Level Beta Power") + ylab("Delta Power")+
  theme_classic()+
  theme(axis.title=element_text(size=16),
        axis.text=element_text(size=14),
        strip.text=element_text(size=14))

ggplot(data = DBlong, aes(x=PBeta_state, y=ParietalDelta, color=BI))+
  geom_smooth(method="lm", fullrange=TRUE, na.rm = T, se=F)+
  scale_color_viridis_d("BI",end = .9)+
  xlab("State-Level Beta Power") + ylab("Delta Power")+
  theme_classic()+
  theme(axis.title=element_text(size=16),
        axis.text=element_text(size=14),
        strip.text=element_text(size=14))
  

```


Parietal synchrony and BI
```{r}
model1_fit <- lmer(formula = ParietalDelta ~ 1 + PBeta_trait_c + PBeta_state + BI +
                     PBeta_trait_c:BI + PBeta_state:BI + PBeta_trait_c:PBeta_state + 
                     PBeta_trait_c:PBeta_state:BI+
                      (1 + PBeta_state|id), 
                    data=DBlong,
                    na.action=na.exclude)
summary(model1_fit)
```



Visualizing synchrony and BI
```{r}
DBlong$BI<-as.factor(DBlong$BI)
library(dplyr)

DBlong%>%
  dplyr::group_by(id)%>%
  ggplot(aes(x=FrontalBeta,y=FrontalDelta, color=BI, shape=BI)) +
  geom_point(size=4) +
  scale_shape_manual(values=c(1,4))+
  scale_color_viridis_d("BI",end = .9)+
  stat_smooth(method="lm", fullrange=TRUE, na.rm = T) +
  xlab("Beta Power") + ylab("Delta Power") + 
  theme_classic()+
  theme(axis.title=element_text(size=16),
        axis.text=element_text(size=14),
        strip.text=element_text(size=14))+
  facet_wrap(.~BI)
```


# Delta-Beta Synchrony and social anxiety
Multilevel models examining if and how between person differences in Social Anxiety are related to within or between-person synchrony

Social Anxiety and Frontal synchrony
```{r}
model1_fit <- lmer(formula = FrontalDelta ~ 1 + FBeta_trait_c + FBeta_state + BIQ.c + ScaredSoc.c +
                     FBeta_trait_c:ScaredSoc.c + FBeta_state:ScaredSoc.c + FBeta_trait_c:FBeta_state +
                     FBeta_trait_c:FBeta_state:ScaredSoc.c +
                      (1 + FBeta_state|id), 
                    data=DBlong,
                    na.action=na.exclude)
summary(model1_fit)
```


Social Anxiety and Central synchrony
```{r}
model1_fit <- lmer(formula = CentralDelta ~ 1  + CBeta_trait_c + CBeta_state + BIQ.c + ScaredSoc.c +
                     CBeta_trait_c:ScaredSoc.c + CBeta_state:ScaredSoc.c + CBeta_trait_c:CBeta_state + 
                     CBeta_trait_c:CBeta_state:ScaredSoc.c+
                      (1 + CBeta_state|id), 
                    data=DBlong,
                    na.action=na.exclude)
summary(model1_fit)
```

Social Anxiety and Parietal synchrony
```{r}
model1_fit <- lmer(formula = ParietalDelta ~ 1 + PBeta_trait_c + PBeta_state + BIQ.c +ScaredSoc.c +
                     PBeta_trait_c:ScaredSoc.c + PBeta_state:ScaredSoc.c + PBeta_trait_c:PBeta_state + 
                     PBeta_trait_c:PBeta_state:ScaredSoc.c+
                      (1 + PBeta_state|id), 
                    data=DBlong,
                    na.action=na.exclude)
summary(model1_fit)
```



# Specificity of social anxiety at Frontal and Central Regions

Frontal synchrony 
```{r}
#separation anxiety
model1_fit <- lmer(formula = FrontalDelta ~ 1  + FBeta_trait_c + FBeta_state + ScaredSep.c +
                     FBeta_trait_c:ScaredSep.c + FBeta_state:ScaredSep.c + FBeta_trait_c:FBeta_state +
                     FBeta_trait_c:FBeta_state:ScaredSep.c +
                      (1 + FBeta_state|id), 
                    data=DBlong,
                    na.action=na.exclude)
summary(model1_fit)

#general anxiety
model1_fitG <- lmer(formula = FrontalDelta ~ 1  + FBeta_trait_c + FBeta_state + ScaredGen.c +
                     FBeta_trait_c:ScaredGen.c + FBeta_state:ScaredGen.c + FBeta_trait_c:FBeta_state +
                     FBeta_trait_c:FBeta_state:ScaredGen.c +
                      (1 + FBeta_state|id), 
                    data=DBlong,
                    na.action=na.exclude)
summary(model1_fitG)
 
```

Central synchrony
```{r}
#separation anxiety
model1_fit <- lmer(formula = CentralDelta ~ 1 + CBeta_trait_c + CBeta_state + ScaredSep.c +
                     CBeta_trait_c:ScaredSep.c + CBeta_state:ScaredSep.c + CBeta_trait_c:CBeta_state + 
                     CBeta_trait_c:CBeta_state:ScaredSep.c+
                      (1 + CBeta_state|id), 
                    data=DBlong,
                    na.action=na.exclude)
summary(model1_fit)

#general anxiety
model1_fitG <- lmer(formula = CentralDelta ~ 1  + CBeta_trait_c + CBeta_state + ScaredGen.c +
                     CBeta_trait_c:ScaredGen.c + CBeta_state:ScaredGen.c + CBeta_trait_c:CBeta_state + 
                     CBeta_trait_c:CBeta_state:ScaredGen.c+
                      (1 + CBeta_state|id), 
                    data=DBlong,
                    na.action=na.exclude)
summary(model1_fitG)
```

# Visualization of social anxiety effects

After testing the Social anxiety specificity to the Frontal region, we can plot these slopes to see individual differences across our sample

```{r, echo=FALSE}
ggplot(data=DBlong[which(DBlong$id <= 3097),], aes(x=FBeta_state,y=FrontalDelta, color=SCARED_P_psocphf_P_BLN)) +
  geom_point() +
  scale_color_viridis_c()+
  stat_smooth(method="lm", fullrange=TRUE, na.rm = T) +
  xlab("Individual Variation in Beta Power") + ylab("Delta Power") + 
  facet_wrap( ~ id, scales = "free") +
  theme_classic()+
  theme(axis.title=element_text(size=16),
        axis.text=element_text(size=14),
        strip.text=element_text(size=14))
```


We can also plot our sample-level effects for Central power
```{r, echo=FALSE}
DBlong<-DBlong%>%
  group_by(id) %>%
  dplyr::mutate(SAcat=mean(SCARED_P_psocphf_P_BLN, na.rm=TRUE))

DBlong$SAcat<-cut(DBlong$SAcat, c(0,4,13))


                  
ggplot(data=DBlong, aes(x=CBeta_trait,y=CDelta_trait, color=SAcat)) +
  geom_point(size=4) +
  scale_color_viridis_d("Social Anxiety",end = .9)+
  stat_smooth(method="lm", fullrange=TRUE, na.rm = T) +
  xlab("Trait Level Variation in Beta Power") + ylab("Delta Power") + 
  theme_classic()+
  theme(axis.title=element_text(size=16),
        axis.text=element_text(size=14),
        strip.text=element_text(size=14))
```


Johnson-Neyman plot of the interactions
```{r}
#inspecting data structure to vectorize matrix variables
str(DBlong)
DBlong$ScaredSoc.c<-as.vector(DBlong$ScaredSoc.c)

#Re-running model under lm4 command
model2a_fit <- lme4::lmer(formula = FrontalDelta ~ 1 + seconds + FBeta_trait_c + FBeta_state + SCARED_P_psocphf_P_BLN +
                     FBeta_trait_c:SCARED_P_psocphf_P_BLN + FBeta_state:SCARED_P_psocphf_P_BLN + FBeta_trait_c:FBeta_state +
                     FBeta_trait_c:FBeta_state:SCARED_P_psocphf_P_BLN +
                      (1 + FBeta_state|id), 
                    data=DBlong,
                    na.action=na.exclude)
summary(model2a_fit)
```



Get confidence intervals for both fixed and random effects
```{r}
confint(model2a_fit)
  
# Save predicted scores
DBlong$pred_m2a <- predict(model2a_fit)

# Fit statistics  
AIC(logLik(model2a_fit)) 
BIC(logLik(model2a_fit))
logLik(logLik(model2a_fit))
```


Plotting and probing the simple slopes (within-person association between Beta Power states and Delta Power) across the full range of the moderator (Social Anxiety).

```{r, echo=FALSE}
johnson_neyman(model=model2a_fit, pred=FBeta_state, modx=SCARED_P_psocphf_P_BLN, 
               sig.color = "#350a63", insig.color = "#69c90e", alpha = 0.016,
               title = "State-Level Delta-Beta Synchrony Across Levels of Anxiety")

interact_plot(model2a_fit, pred = FBeta_state, modx = SCARED_P_psocphf_P_BLN, interval = FALSE, plot.points = TRUE, colors = "Qual3", x.label = "Beta Power individual states", y.label = "Delta Power", legend.main = "Anxiety Scores", )

```

Fitting the between-level differences
```{r}
model2a_fit <- lme4::lmer(formula = CentralDelta ~ 1 + seconds + CBeta_trait_c + CBeta_state + SCARED_P_psocphf_P_BLN + 
                     CBeta_trait_c:SCARED_P_psocphf_P_BLN + CBeta_state:SCARED_P_psocphf_P_BLN + CBeta_trait_c:CBeta_state + 
                     CBeta_trait_c:CBeta_state:SCARED_P_psocphf_P_BLN+
                      (1 + CBeta_state|id), 
                    data=DBlong,
                    na.action=na.exclude)
summary(model2a_fit)
```